%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\thispagestyle{empty}
\header{nicolas}{fishman}
       {}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    (919) 995-1050
    \href{mailto:njwfish@gmail.com}{njwfish@gmail.com}
    \href{mailto:njwfish@stanford.edu}{njwfish@stanford.edu}
    \href{http://njw.fish}{njw.fish}
    %\vspace{10pt}
  \section{programming}
    {\color{red} $\varheartsuit$} C++, Java, Python
    Matlab, R
    Javascript, PHP
    CSS3 \& HTML5
    MySQL, MongoDB
    %\vspace{10pt}
  \section{languages}
    bilingual spanish/english
\end{aside}

\section{interests}

machine learning, bioinformatics, cryptography, privacy

\section{education}

\begin{entrylist}
  \entry
    {since 2017}
    {Computer Science and Bioengineering Major}
    {Stanford University, Stanford, CA}
    {Focusing on machine learning applications in genetic engineering.}

  \entry
    {2016 - 2017}
    {Classes in Computer Science}
    {George Washington University, Washington, DC}
    {Cryptography with Prof. Valerie Nelson, Grade Earned: A\\
     Bioinformatics with Prof. Keith Cranston, Grade Earned: A\\
     Machine Learning with Prof. Claire Monteleoni, Grade Earned: A}
     
  \entry
    {2015 - 2016}
    {Classes in Mathematics}
    {Stanford University, Stanford, CA}
    {Multivar. Integral Calc. with Prof. Margarita Kanarsky, Grade Earned: A\\
     Multivar. Differential Calc. with Prof. Margarita Kanarsky, Grade Earned: A}
    
  \entry
    {2013 - 2017}
    {High School Diploma}
    {Woodrow Wilson High School, Washington, DC}
    {GPA: 4.5 \\
    Science, Mathematics and Technology Scholar of Excellence, \\Information Technology Student}

\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2017}
    {Technical Specialist}
    {Star Lab Corporation}
    {Developing game theory and machine learning models to research how to defend and attack embedded systems.}
    
  \entry
    {2016  - 2017}
    {Research Fellow}
    {Comparative Genomics Section, National Institutes of Health}
    {Storage and analysis of structural variants, continued work on DOGSV. Prostate cancer tumor classification from variant statistics. Determining if tumors are BRCA1, BRCA2, or FASTA, among other types, based on frequency and ratios of both single nucleotide and structural variations. }
  \entry
    {2016}
    {IRTA Intern}
    {Comparative Genomics Branch, NHGRI/ NIH}
    {Responsible for designing and implementing a database framework to facilitate access and analysis of structural variants, originally only for internal lab use, currently in the process of becoming a public resource. See DOGSV}
  \entry
    {2016 - 2017}
    {Founder}
    {Science Olympiad Team, Woodrow Wilson High School}
    {Connected available funding and available expertise to expand opportunity.}
  \entry
    {2016 - 2017}
    {President}
    {National Honor Society, Woodrow Wilson High School}
    {Providing tutoring and organizing community service projects.}
  \entry
    {2015 - 2017}
    {President}
    {FIRST Robotics Team 2914, Woodrow Wilson High School}
    {Managing a budget of \$20,000, applying for 6 grants, totaling over \$10,000 dollars to pay for team equipment and travel.}


\end{entrylist}

\begin{entrylist}
  \entry
    {2015 - 2016}
    {Tutor}
    {Georgetown University, George Washington University}
    {Advanced Mathematics and Computer Science, all students received A's or B's on final exams.}
  \entry
    {2014 - 2015}
    {Localization Developer}
    {Open Medical Record System}
    {Facilitating ease of translation across a large medical record system.}
  \entry
    {2014 - 2017}
    {Lead Programmer}
    {FIRST Robotics Team 2914, Woodrow Wilson High School}
    {Overseeing robot code development, creation of Python based vision system in 2014, development of working Kalmann filter for robot location tracking in 2015 and 2016. Prediction using neural networks of FRC games in 2016 and 2017.}
  \entry
    {2014 - 2017}
    {Web Developer}
    {The Wilson Beacon, Woodrow Wilson High School}
    {Website redesign and performance improvements. \href{http://thewilsonbeacon.com}{thewilsonbeacon.com}}
\end{entrylist}


\section{projects}

\begin{entrylist}
  \entry
    {2017}
    {Fleeing from Terror}
    {Stanford University}
    {Won CS 109 competition for developing a way to make public spaces safer. Outlined a methodology for evaluating a room on the basis of safety, using the time for a room to evacuate in the case of a sudden terrifying event as our metric of safety. Also developed a way to optimize the design of a room for safety, and proposed a regulatory framework for ensuring new construction is safe.}

  \entry
    {2016 - 2017}
    {DOGSV}
    {Comparative Genomics Branch, National Institutes of Health}
    {Built database for the storage and analysis of hundreds of millions of structural variants. Trained model to cluster variants and assess the likelihood of variants being false positives.}
    
  \entry
    {2017}
    {Predict Population Diversity from Unassembled Reads} 
    {GWU}
    {Developed model to estimate the genetic diversity of viruses with high rates of nucleotide substitution, using a nearest neighbor regression on k-mer analyses of the raw reads.}
    
    \entry
    {2017}
    {Predict Outcomes in Fantasy Baseball} 
    {George Washington University}
    {Developed model to predict outcomes in fantasy baseball by building a dataset of MLB player histories, and then proving the validity of using player histories to predict team outcomes.}

  \entry
    {2016}
    {Legal Aid Dashboard} 
    {Drupal Legal Aid}
    {Using Google web traffic data for various legal aid websites, classified the topics of the most popular web pages by location to facilitate allocation of legal aid resources to meet need.}
\end{entrylist}

\section{honors}
\begin{entrylist}
    \entry
    {2017}
    {G.R.E.A.T. Award}
    {NHGRI, National Institutes of Health}
    {The Genome Recognition of Employee Accomplishments and Talents (G.R.E.A.T) Award, given for work in the Ostrander lab on the DOGSV system for storing and analyzing structural variants.}
    \entry
    {2017}
    {National AP Scholar}
    {The College Board}
    {For earning an average score of at least 4 on all AP Exams taken, and scores of 4 or higher on eight or more of these exams.}
    \entry
    {2017}
    {Science Fair First Place Winner}
    {Woodrow Wilson High School}
    {Top prize in school wide science fair for machine learning applications in predicting population diversity from genomic kmer analysis.}
  \entry
    {2016}
    {Science, Mathematics, and Technology Scholar}
    {Woodrow Wilson High School}
    {For the completion of the requisite courses and the completion of a final project.}
  \entry
    {2016}
    {National Hispanic Recognition Program}
    {The College Board}
    {Awarded to the top performing hispanic high school students.}
  \entry
    {2016}
    {Judges' Award}
    {FIRST Robotics}
    {For mentorship and tutoring programs developed in 2016.}
  \entry
    {2014}
    {Innovation and Control Award}
    {FIRST Robotics}
    {For a vision processing system written in Python.}
  \entry
    {2013}
    {Honor Roll}
    {Woodrow Wilson High School}
    {For receiving a GPA over 3.0. Earned every semester.}
\end{entrylist}

\section{service}
\begin{entrylist}
  \entry
    {2015 - 2017}
    {National Honor Society}
    {Woodrow Wilson High School}
    {Mathematics, history, English, computer science and physics tutoring.}
  \entry
    {2014 - 2017}
    {Invasive Species Management}
    {Rock Creek Conservancy}
    {Certified volunteer leader for the Rock Creek Conservancy and National Park Service.}
  \entry
    {2013}
    {IT Instructor}
    {Dominican Republic}
    {Designing and teaching a cirriculuum focussed on teaching foundational IT skills: how to use email, Microsoft Word, Google for communications and research. Taught in Spanish.}
\end{entrylist}

\section{publications}

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
\printbibsection{article}{article in peer-reviewed journal}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
\end{refsection}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
\end{refsection}

\printbibsection{misc}{presentations}
\printbibsection{report}{research reports}
\printbibsection{article}{abstracts}

\end{document}
